\documentclass[12pt]{amsart}
\usepackage{amsaddr}
\usepackage{marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage{svmacro}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{enumitem}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 104: Multivariable Calculus }
\author{Midterm \\ Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

%\author{Co-author}
%\address{  }
%\email {  }
%
\date{\today}

\begin{document}

\maketitle

There are four questions. Make sure you justify all your work for complete credit.

\section*{Rules}

\begin{itemize}[leftmargin=*]
	\item You have 80  minutes to complete your work..
	\item Closed books.
	\item No use of internet, textbooks, computer algebra systems, calculators.
	\item No collaboration.
	\item 1 person per bathroom break. When you go to the bathroom, turn in your cellphone and exam until return.
\end{itemize}


Scores:
\begin{enumerate}
	\item \_\_\_\_
	\item \_\_\_\_
	\item \_\_\_\_
	\item \_\_\_\_
	\item[Total]: \_\_\_\_
\end{enumerate}

\newpage

\section*{Questions}
\begin{problem}[20 points, 5 points each]
\begin{enumerate}
	\item Where does the line
	      \begin{equation*}
		      x(t) = 2t-1 \,; y(t) = 3t + 2 \,; z(t) = 4t
	      \end{equation*}
	      intersect the plane given by $4x + 3y - z = 3$?
	      \vspace{7cm}

	\item What is the surface that the following function a parametrization of?
	      Give a reason.
	      \begin{equation*}
		      G(\varphi, \theta) = \begin{bmatrix}
			      R \cos \theta \sin \varphi \\
			      R \sin \theta \sin \varphi \\
			      R \cos \varphi
		      \end{bmatrix}
	      \end{equation*}

	      \vspace{7cm}

	      \newpage

	\item
	      What is the value of $c$ so that the planes
	      $2cx - y + c^2z = 15$ and $x + 5cy - 3z = 4$ are orthogonal?
\end{enumerate}
\end{problem}


\newpage

\begin{problem}[20 points]
\begin{enumerate}
	\item Find an equation of the tangent plane to the surface $z= x \sin(x+y)$ at the point $(-1,1,0)$.
	      \vspace{8cm}
	\item Find the linear approximation at $(0,0)$ of
	      $e^x \cos(xy)$.
\end{enumerate}
\end{problem}
\newpage


\begin{problem}[20 points]
Given the curve  $\gamma(t) = (1, t, t^2)$.
\begin{enumerate}
	\item Compute the velocity, acceleration of $\gamma$ at time $t=1$.
	\item What is the arclength of $\gamma$ from $t=1$ to $t=2$?
\end{enumerate}
\end{problem}

\newpage

\begin{problem}[20 points]
A manufacturer has modeled its yearly production function $P$  as a Cobb-Douglas function
$$
	P(L, K)= 2 L^{0.2} K^{0.8}
$$
where $L$ is the number of labor hours (in thousands) and $K$ is the invested capital (in millions of dollars).
Suppose the manufacturer has 20 workers and 2 machines.
\begin{enumerate}
	\item Use differentials to estimate the change in production if the company want to employ only 15 workers and increase to 3 machines.
	      \vspace{6cm}
	\item Compare the above result to the exact change (not the differential approximation).
	      \vspace{6cm}
\end{enumerate}
\end{problem}

\printbibliography
%\bibliography{refs}
%\bibliographystyle{halpha-abbrv}


\end{document}
