\documentclass[12pt]{amsart}
\usepackage{amsaddr}
\usepackage{marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage{svmacro}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{enumitem}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 104: Multivariable Calculus }
\author{Final\\ Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

%\author{Co-author}
%\address{  }
%\email {  }
%
\date{\today}

\begin{document}

\maketitle

There are four questions. Make sure you justify all your work for complete credit.

\section*{Rules}

\begin{itemize}[leftmargin=*]
	\item You have 80  minutes to complete your work..
	\item Closed books.
	\item No use of internet, textbooks, computer algebra systems, calculators.
	\item No collaboration.
	\item 1 person per bathroom break. When you go to the bathroom, turn in your cellphone and exam until return.
\end{itemize}


Scores:
\begin{enumerate}
	\item \_\_\_\_
	\item \_\_\_\_
	\item \_\_\_\_
	\item[Total]: \_\_\_\_
\end{enumerate}

\newpage

\section*{Questions}
\begin{problem}[20 points, 10 points each]
Evaluate
\begin{enumerate}
	\item
	      \begin{equation*}
		      \iiint_E y \, dV \,,
	      \end{equation*}
	      where $E = \set{ (x,y,z) | 0 \leq x \leq 3\,, 0\leq y \leq x \,, x - y \leq z \leq x+y  } $.

	      \vspace{8cm}

	\item The volume of solid enclosed by the paraboloid $z = (x-2)^2 + (y-2)^2$ and the plane $ z  = 4$.


\end{enumerate}
\end{problem}

\newpage

\begin{problem}[30 points, 10 points each]
Evaluate the integrals
\begin{enumerate}
	\item \begin{equation*}
		      \int_{-\infty}^\infty e^{-x^2} \, dx \,.
	      \end{equation*}
	      \vspace{8cm}

	\item \begin{equation*}
		      \iint_D \sin\sqrt{x^2 + y^2} \, dA
	      \end{equation*}
	      where $D$ is the upper half of the disk center at the origin and radius 4.
	      \vspace{8cm}

	\item \begin{equation*}
		      \int_0^2 \int_0^{\sqrt{2x - x^2}} \sqrt{x^2 + y^2} \, dy dx \,.
	      \end{equation*}
\end{enumerate}
\end{problem}
\newpage

\begin{problem}[50 points, 25 each]
\begin{enumerate}
	\item
	      The total production $P$ of a certain product depends on the amount $L$ of labor used and the amount $K$ of capital investment.
	      The Cobb-Douglas model $P = bL^{\alpha}K^{1-\alpha}$ follows from certain economic assumptions, where $b$ and $\alpha$ are positive constants and $\alpha < 1$. If the cost of a unit of labor is $m$ and the cost of a unit of capital is $n$, and the company can spend only $p$ dollars as its total budget, then maximizing the production $P$ is subject to the constraint $mL + nK = p$. Show that the maximum production occurs when
	      \[
		      L = \frac{\alpha p}{m} \quad \text{and} \quad K = \frac{(1 - \alpha)p}{n}
	      \]
	      \newpage

	\item Suppose that the production is fixed at $bL^{\alpha}K^{1-\alpha} = Q$, where $Q$ is a constant. What values of $L$ and $K$ minimize the cost function $C(L, K) = (mL)^2 + (nK)^3$?
\end{enumerate}
\end{problem}









\printbibliography
%\bibliography{refs}
%\bibliographystyle{halpha-abbrv}


\end{document}
