\documentclass[12pt]{amsart}
\usepackage{amsaddr}
\usepackage{marktext} 
%% Remove draft for real article, put twocolumn for two columns
\usepackage{svmacro}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{enumitem}

%% commentary bubble
\newcommand{\SV}[2][]{\sidenote[colback=green!10]{\textbf{SV\xspace #1:} #2}}

%% Title 
\title{ MATH 104: Multivariable Calculus }
\author{Midterm \\ Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

%\author{Co-author}
%\address{  }
%\email {  }
%
\date{\today}

\begin{document}

\maketitle

There are five questions. Make sure you justify all your work for complete credit.

\section*{Rules}

\begin{itemize}[leftmargin=*]
    \item You have 80  minutes to complete your work..
    \item Closed books.
    \item No use of internet, textbooks, computer algebra systems, calculators. 
    \item No collaboration.
    \item 1 person per bathroom break. When you go to the bathroom, turn in your cellphone and exam until return.
\end{itemize}


Scores:
\begin{enumerate}
    \item \_\_\_\_
    \item \_\_\_\_
    \item \_\_\_\_
    \item \_\_\_\_
    \item \_\_\_\_
    \item[Total]: \_\_\_\_
\end{enumerate}

\newpage

\section*{Questions}
\begin{problem}[20 points, 5 points each]
    \begin{enumerate}
        \item Where does the line 
    \begin{equation*}
        x(t) = 2t-1 \,; y(t) = 3t + 2 \,; z(t) = 4t
    \end{equation*}
    intersect the plane given by $4x + 3y - z = 3$?
    \vspace{7cm}

\item What is the surface that the following function a parametrization of?
        Give a reason.
    \begin{equation*}
        G(\varphi, \theta) = \begin{bmatrix}
            R \cos \theta \sin \varphi \\
            R \sin \theta \sin \varphi \\
            R \cos \varphi
        \end{bmatrix}
    \end{equation*}

    \vspace{7cm}

    \newpage
\item 
    In $\R^4$, what is the intersection of the $(x_1, x_2)$ and $(x_3, x_4)$ plane?

    \vspace{10cm}

\item 
    What is the value of $c$ so that the planes
    $2cx - y + c^2z = 15$ and $x + 5cy - 3z = 4$ are orthogonal?
    \end{enumerate}
\end{problem}

\newpage

\begin{problem}[20 points, 5 points each]
    Consider the following functions
    \begin{equation*}
        f(u,v,w) = \begin{pmatrix}
            u^2 v^{-3} w \\ 2u - 5w \\ uv - vw
        \end{pmatrix} \,,
    \end{equation*}
    and
    \begin{equation*}
        g(a,b,c) = 
        \begin{pmatrix}
            \ln (ab) \\
            abc \\
            b^2 + 5c
        \end{pmatrix} \,,
    \end{equation*}
    \begin{enumerate}
        \item Compute the derivative of $f$ at the point $(1, -1, 2)$.
        \item What is the most sensitive output of $f$ at the point $(1, -1, 2)$?
        \item Compute $[Dg]_{(a,b,c)}$.
        \item Compute the derivative of $g\circ f$ at the point $(1, -1, 2)$.
    \end{enumerate}
\end{problem}

\newpage

\begin{problem}[20 points]
    \begin{enumerate}
        \item Find an equation of the tangent plane to the surface $z= x \sin(x+y)$ at the point $(-1,1,0)$.
            \vspace{8cm}
        \item Find the linear approximation at $(0,0)$ of
            $e^x \cos(xy)$.
    \end{enumerate}
\end{problem}
 \newpage


\begin{problem}[20 points]
    Given the curve  $\gamma(t) = (\sin t, \cos 3t, t^2)$.
    \begin{enumerate}
        \item Compute the velocity, acceleration of $\gamma$ at time $t=1$.
        \item What is the arclength of $\gamma$ from $t=1$ to $t=2$?
    \end{enumerate}
\end{problem}

\newpage

\begin{problem}[20 points]
    A manufacturer has modeled its yearly production function $P$ (the value of its entire production, in millions of dollars) as a Cobb-Douglas function
$$
P(L, K)=1.47 L^{0.65} K^{0.35}
$$
where $L$ is the number of labor hours (in thousands) and $K$ is the invested capital (in millions of dollars). Suppose that when $L=30$ and $K=8$, the labor force is decreasing at a rate of 2000 labor hours per year and capital is increasing at a rate of $\$ 500,000$ per year. Find the rate of change of production.
\end{problem}

\printbibliography 
%\bibliography{refs}
%\bibliographystyle{halpha-abbrv}


\end{document}
